\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm,tabu,enumerate,tikz}
\usepackage[margin=1in]{geometry}
\usepackage{verbatim} % Allows Multi-line comments 
\usepackage{multicol}
\usetikzlibrary{automata,positioning}
\newcommand{\encode}[1]{\langle #1 \rangle}
\usepackage[parfill]{parskip}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{indentfirst}

\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}

\title{Robotics Club Week 1}
\author{David Cobbley }
\date{September 2016}

\begin{document}

\maketitle

\section{Agenda}
\begin{itemize}
    
    \item Welcome Programmers
    \item Introductions - Mentors \& Students
    \item Select note taker
    \item RoboRio
    \item Languages available for FRC
    \item Why we switched to Java
    \item Solar flare \& previous robots
    \item How all groups play together
    \item Java environment
    \item Koans
\end{itemize}

\section{welcome}
These are the most important links you will need. Everything you want to know can be found here.
\begin{itemize}
    \item[] \url{http://glencoerobotics.com/forum/}
    \item[] \url{https://www.chiefdelphi.com/forums/portal.php}
    \item[] \url{http://wpilib.screenstepslive.com/s/4485}
\end{itemize}

\section{Programming Groups}
\begin{itemize}
    
    \item Robot
    \item Apps
\end{itemize}
Don't have to stick to a group

\pagebreak

\section{Skills we teach}
\begin{enumerate}
    \item Code Collaboration - pair programming
    \item analyzing problems
    \item how a computer thinks
    \item incorporating math into code
    \item Working with people outside your domain - Electrical and mech.
    \item learning how to learn a language
    \item Leaning Java (Notice this is last)
\end{enumerate}


\section{RoboRio}
\begin{itemize}
\item[] \url{https://wpilib.screenstepslive.com/s/4485/m/13503/c/86641}
\item[] \url{http://www.ni.com/pdf/manuals/374474a.pdf}
\item[] \url{https://decibel.ni.com/content/docs/DOC-30419}
\end{itemize}

\section{Languages for FRC}
\subsection{java}
\begin{itemize}
\item[] \url{https://wpilib.screenstepslive.com/s/4485/m/13503/l/599679-installing-eclipse-c-java}
\item[] \url{https://www.chiefdelphi.com/forums/archive/index.php/t-128134.html}
\end{itemize}

\subsection{C++}
\begin{itemize}
\item[] \url{https://wpilib.screenstepslive.com/s/4485/m/13503/l/599679-installing-eclipse-c-java}
\item[] \url{https://www.reddit.com/r/FRC/comments/4k24cu/java_vs_c/}
\end{itemize}

\subsection{Other}
\begin{itemize}
\item[] \url{https://github.com/robotpy/pyfrc}
\end{itemize}

\section{Why we use Java}
\begin{itemize}
    \item Better visibility across mentors to assist students.
    \item Code checkins - pull requests.
    \item Continuous integration build capabilities.
    \item Fast enough for what we need to do.
    \item Wpilib abstracts all the difficult DIO etc. away allowing students to focus on programming paradigm.
\end{itemize}

\pagebreak
\section{Robots}
\subsection{Eclipse}
\begin{itemize}
\item[] \url{http://www.thebluealliance.com/team/4488/2016}
\item[] \url{https://www.youtube.com/watch?v=oxOSjQpTp3U}
\item[] \url{https://www.youtube.com/watch?v=9WOQbL9n4Cs}
\end{itemize}
\subsection{Solar Flare}
\begin{itemize}
\item[] \url{http://www.thebluealliance.com/team/4488/2015}
\item[] \url{https://www.youtube.com/watch?v=VpZazV3wP1s}
\end{itemize}
\subsection{Wildfire}
\begin{itemize}
\item[] \url{http://www.thebluealliance.com/team/4488/2014}
\item[] \url{https://www.youtube.com/watch?v=tEhQnKbRz-0}
\item[] \url{https://www.youtube.com/watch?v=lmtvsggl81M}
\end{itemize}
\subsection{Phantom}
\begin{itemize}
\item[] \url{http://www.thebluealliance.com/team/4488/2013}
\end{itemize}



\section{Camera}
We currently use a logitech c920 with a kangaroo mobile computer to perform the vision processing.

\section{How groups interact}
Mechanical, Electrical, Business, and Apps are all required. Without them we would have nothing to program.

\section{Java Environment}
We use Eclipse with the NI driver station.

\begin{itemize}
\item[] \url{https://wpilib.screenstepslive.com/s/4485/m/13503/l/599679-installing-eclipse-c-java}
\item[] \url{https://wpilib.screenstepslive.com/s/4485/m/13503/l/599677-frc-driver-station-powered-by-ni-labview}
\end{itemize}

\section{Koans}
\begin{itemize}
\item[] \url{https://github.com/dcobbley/roboticsClubSeason/blob/master/Koans.pdf}
\end{itemize}

\section{Extras}
\begin{itemize}
\item[] \url{https://www.youtube.com/watch?v=nZf9F-3QKMw}
\item[] \url{https://www.youtube.com/watch?v=Qfe-zs2f2EM}
\end{itemize}


\end{document}

